Baseline Drift Estimation for Air Quality Data Using Quantile Trend Filtering

### 2019-04-18 Manuscript/detrendify_aoas.tex
updated notation for consensus update

The augmented Lagrangian is given by
\begin{eqnarray*}
	\mathcal{L}(\M{\Theta}, \{\Mn{\Theta}{w}\}, \{\Mn{\Omega}{w}\}) & = & \sum_{w=1}^W \mathcal{L}_w(\M{\Theta}, \Mn{\Theta}{w}, \Mn{\Omega}{w}),
\end{eqnarray*}
where
\begin{eqnarray*}
	\mathcal{L}_w(\M{\Theta}, \Mn{\Theta}{w}, \Mn{\Omega}{w}) & = & \sum_{j=1}^J \biggl [\rho_{\tau_j}(\Vn{y}{w} - \Vn{\theta}{w}_j)+\lambda_j \lVert \Mn{D}{k+1}\Vn{\theta}{w}_j\rVert_1 \\
	&& + \; (\Vn{\theta}{w}_j - \Mn{U}{w}\V{\theta}_{j})\Tra\Vn{\omega}{w}_{j} +
	\frac{\gamma}{2}\lVert \Vn{\theta}{w}_j - \Mn{U}{w}\V{\theta}_{j}\rVert_2^2 \biggr ] + \iota_\mathcal{C}(\Mn{\Theta}{w}),
\end{eqnarray*}
where $\gamma$ is a positive penalty parameter.

@@

{\bf Updating $\M{\Theta}$: } Some algebra shows that updating the consensus variable step is computed as follows.

\begin{eqnarray}
\label{eq:update_consensus}
~~~~\ME{\theta}{ij}	 &=& \begin{cases}
\frac{1}{2}\left (\MnE{\theta}{w-1}{ij} + \MnE{\theta}{w}{ij} \right)
-
\frac{1}{2\gamma} \left (\MnE{\omega}{w-1}{ij} + \MnE{\omega}{w}{ij} \right)
& \mbox{if~} l_{w} \le i \le u_{w-1},  \\
\MnE{\theta}{w}{ij} & \mbox{if~} u_{w-1} < i \le l_{w+1}  \\
\frac{1}{2} \left ( \MnE{\theta}{w}{ij} + \MnE{\theta}{w+1}{ij} \right )
-
\frac{1}{2\gamma}	\left (\MnE{\omega}{w}{ij} + \MnE{\omega}{w+1}{ij} \right )
& \mbox{if~} l_{m+1} < i \le u_{m}
\end{cases},
\end{eqnarray}

>>>>

The augmented Lagrangian is given by
\begin{eqnarray*}
	\mathcal{L}(\M{\Theta}, \{\Mn{\Theta}{w}\}, \{\Mn{\Omega}{w}\}) & = & \sum_{w=1}^W \mathcal{L}_w(\M{\Theta}, \Mn{\Theta}{w}, \Mn{\Omega}{w}),
\end{eqnarray*}
where
\begin{eqnarray*}
	\mathcal{L}_w(\M{\Theta}, \Mn{\Theta}{w}, \Mn{\Omega}{w}) & = & \sum_{j=1}^J \biggl [\rho_{\tau_j}(\Vn{y}{w} - \Vn{\theta}{w}_j)+\lambda_j \lVert \Mn{D}{k+1}\Vn{\theta}{w}_j\rVert_1 \\
	&& + \; (\Vn{\theta}{w}_j - \Mn{U}{w}\V{\theta}_{j})\Tra\Vn{\omega}{w}_{j} +
	\frac{\gamma}{2}\lVert \Vn{\theta}{w}_j - \Mn{U}{w}\V{\theta}_{j}\rVert_2^2 \biggr ] + \iota_\mathcal{C}(\Mn{\Theta}{w}),
\end{eqnarray*}
where $\gamma$ is a positive tuning parameter.

@@

{\bf Updating $\M{\Theta}$: } Some algebra shows that,  defining $i_w = i-l_w+1$, updating the consensus variable step is computed as follows.

\begin{align}
\label{eq:update_consensus}
~~~~\ME{\theta}{ij}	 &=& \begin{cases}
\frac{1}{2}\left (\MnE{\theta}{w-1}{i_{w-1}j} + \MnE{\theta}{w}{i_wj} \right)
-
\frac{1}{2\gamma} \left (\MnE{\omega}{w-1}{i_{w-1}j} + \MnE{\omega}{w}{i_{w}j} \right)
& \mbox{if~} l_{w} \le i \le u_{w-1},  \\
\MnE{\theta}{w}{i_{w}j} & \mbox{if~} u_{w-1} < i \le l_{w+1}  \\
\frac{1}{2} \left ( \MnE{\theta}{w}{i_{w}j} + \MnE{\theta}{w+1}{i_{w+1}j} \right )
-
\frac{1}{2\gamma}	\left (\MnE{\omega}{w}{i_{w}j} + \MnE{\omega}{w+1}{i_{w+1}j} \right )
& \mbox{if~} l_{w+1} < i \le u_{w}
\end{cases},
\end{align}
